\documentclass[12pt]{amsart} 
\usepackage{amsfonts}
\usepackage{amscd}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumitem}
\usepackage{pgf,tikz,tikz-cd}
\usepackage{mathrsfs}
\usepackage[margin=1in]{geometry}
\usepackage{array}
\usepackage{lipsum}
\usepackage{dsfont}
\usepackage{stmaryrd}

%\graphicspath{ {./diagrams/} }

\input{./latex-preamble/cm-preamble.tex}

\newtheorem*{lemma}{Lemma}

\begin{document}

{Hartshorne} \hfill {1-27-2025}

\bigskip\bigskip

\begin{center}

{\sc Chapter II-1}

\end{center}

\begin{center}

  {Noah Parker} %\footnote{Collaborated with Kalev Martinson and Frank :).}}
    
\end{center}

\bigskip

% \begin{enumerate}
% 	\item[1.] {
%     }
% \end{enumerate}
% 
% \begin{proof}
% \end{proof}

\begin{enumerate}
	\item[1.2.] {
      \begin{enumerate}
        \item Let $\vphi:\F\to \G$ be a morphism of sheaves on $X$, and $p\in X$ a point.
          Show that $(\ker\vphi)_p\cong \ker(\vphi_p)$ and $(\im\vphi)_p\cong \im(\vphi_p)$.
        \item Show that $\vphi$ is injective (resp. surjective) if and only if $\vphi_p$ is injective (resp. surjective) for all $p\in X$.
        \item Show that a sequence $\cdots\to \F_{i-1}\xrightarrow{\vphi_{i-1}}\F_i\xrightarrow{\vphi_i}\F_{i+1}\to \cdots$ of sheaves is exact if and only if, for all $p\in X$, the associated sequence of stalks is exact.
      \end{enumerate}
    }
\end{enumerate}

\begin{proof}
  (a) A germ $(s,U)\in (\ker\vphi)_p\subset \F_p$ iff there exists $p\in V\subset U$ with $\vphi(U)(s)|_V = 0$. That is, 
  \begin{align*}
    \vphi_p(s,U) &= (\vphi(V)(s)|_V,V)=(0,V).
  \end{align*}
  Similarly, a germ $(s,U)\in (\im\vphi)_P\subset \G_p$ iff there exists $p\in V\subset U$ with $s|_V= \vphi(V)(t)$. That is,
  \begin{align*}
    (s,U) &= (s|_V,V) = (\vphi(V)(t),V) 
    = \vphi_p(t,V).
  \end{align*}

  (b) $\vphi$ is injective iff $\ker\vphi\cong 0$. The zero map $\ker\vphi\to 0$ is an isomorphism iff each of its localizations $(\ker\vphi)_p\to 0$ are isomorphisms. Using (a), we see that $\vphi$ is injective iff $\ker(\vphi_p)\cong (\ker\vphi)_p\cong 0$, i.e. $\vphi_p$ injective, for all $p\in X$.

  $\vphi$ is surjective iff $\G = \im\vphi$. That is, the inclusion map $i:\im\vphi\to \G$ is an isomorphism.
  This occurs iff each $(\im\vphi)_p\to \G_p$ is an isomorphism, which occurs iff each $\im(\vphi_p)\xrightarrow{\sim} (\im\vphi)_p\to \G_p$ is an isomorphism. 
  This map is the inclusion $\im(\vphi_p)\to \G_p$, so the result follows.

  (c) Consider the following diagram:
  \[
    \begin{tikzcd}[column sep=small,row sep=small]%[column sep= 0.2cm, row sep =0.5cm]
      0\ar[dr]&&0&&0\ar[dr]&&0 \\
      &\ker\vphi_{i-1}\ar[dr]\ar[ur] &&&&\ker\vphi_{i+1}\ar[dr]\ar[ur]\\
      \cdots\ar[ur]\ar[rr]&&\F_{i-1}\ar[rr,"\vphi_{i-1}"]\ar[dr] && \F_i\ar[rr,"\vphi_i"]\ar[ur] && \F_{i+1}\ar[rr,"\vphi_{i+2}"]\ar[dr] &&\cdots \\
                          &&&\ker\vphi_i\ar[ur]\ar[dr]&&&&\ker\vphi_{i+2}\ar[ur]\ar[dr] \\
                          &&0\ar[ur]&&0&&0\ar[ur]&&0
    \end{tikzcd}
  \] 
  Clearly our original diagram is exact if and only if each diagonal $0\to \ker\vphi_i\to \F_i\to \ker\vphi_{i+1}\to0$ is exact.
  Thus, it suffices to show the result for short exact sequences $0\to \F'\xrightarrow{\vphi}\F\xrightarrow{\psi}\F''\to 0$.
  (b) gives us $\vphi$ injective iff each $\vphi_p$ is injective, $\psi$ surjective iff each $\psi_p$ is surjective. 

  If $\im\vphi=\ker\psi$, then this induces natural isomorphisms $\im\vphi_p\cong\ker\psi_p$ for all $p\in X$.
  Inclusions of sheaves induce inclusions of stalks, so $\im\vphi_p=\ker\psi_p$.

  Suppose instead that $\im\vphi_p=\ker\psi_p$ for all $p\in X$, and fix $U\subset X$, $s\in \F'(U)$.
  For each $p\in U$, we have $\wtilde{\im}\vphi_p= \ker\psi_p$, so $\psi_p\vphi_p(s,U)=(0,U)$.
  That is, there is $p\subset V_p\subset U$ such that 
  \[
    \psi(U)\vphi(U)(s)|_{V_p} =0.
  \]
  Then the $V_p$ form a cover of $U$, so the sheaf axiom gives us $\psi(U)\vphi(U)(s)=0$, whence
  \[
    \wtilde{\im}\vphi\subset \ker\psi.
  \] 
  Then, in fact, there is an inclusion $i:\im\vphi\hookrightarrow \ker\psi$ which induces the inclusions $i_p:\im\vphi_p\hookrightarrow\ker\psi_p$ for each $p\in V$.
  The latter inclusions are isomorphisms, so it follows that the former is an isomorphism as well.
  That is,
  \[
    \im\vphi=\ker\psi.
  \] 
\end{proof}

\begin{enumerate}
	\item[1.5.] {
      Show that a sheaf morphism $\vphi:\F\to\G$ is an isomorphism iff it is injective and surjective.
    }
\end{enumerate}

\begin{proof}
  $\vphi$ is an isomorphism iff each $\vphi_p:\F_p\to \G_p$ is an isomorphism. This occurs iff each $\vphi_p$ is injective and surjective, which occurs iff $\vphi$ is injective and surjective by the 2b.
\end{proof}

\begin{enumerate}
	\item[1.8.] {
      Show that, for any $U\subset X$ open, the functor $\Gamma(U,-):\Sh(X)\to \Ab$ is left-exact.
    }
\end{enumerate}

\begin{proof}
  Suppose $0\to \F'\xrightarrow{\vphi}\F\xrightarrow{\psi}\F''\to 0$ is exact.
  Then $\ker(\vphi(U)) = (\ker\vphi)(U)=0$ gives us that $\vphi(U)$ is injective. 
  It suffices to show that $\im(\vphi(U))=\ker(\psi(U))$.
  Since $\ker\psi =\im\vphi = (\wtilde{\im}\vphi)^+$, it suffices to show that $\wtilde{\im}\vphi$ is a sheaf.
  $\vphi(U)$ is injective, so $\vphi(U): \F'(U)\to \wtilde{\im}\vphi(U)$ is an isomorphism of abelian groups.
  Then $\vphi:\F'\to \wtilde{\im}\vphi$ is an isomorphism of presheaves, so $\wtilde{\im}\vphi$ is a sheaf.
\end{proof}

\begin{enumerate}
	\item[1.16.] {
      \emph{Flasque Sheaves}.
      A sheaf $\F$ on a topological space $X$ is \emph{flasque} if for every inclusion $V\subset U$ of open sets, the restriction map $\F(U)\to \F(V)$ is surjective.
      \begin{enumerate}
        \item Show that a constant sheaf on an irreducible topological space is flasque.
        \item If $0\to \F'\to \F\xrightarrow{\vphi} \F''\to 0$ is an exact sequence of sheaves, and if $\F'$ is flasque, then for any open set $U$, the sequence $0\to \F'(U)\to \F(U)\xrightarrow{\vphi} \F''(U)\to 0$ of abelian groups is also exact.
        \item If $0\to \F'\to \F\xrightarrow{\vphi} \F''\to 0$ is an exact sequence of sheaves, and if $\F'$ and $\F$ are flasque, then $\F''$ is flasque.
        \item If $f:X\to Y$ is a continuous map and $\F$ is a flasque sheaf on $X$, then $f_*\F$ is a flasque sheaf on $Y$.
        \item Let $\F$ be any sheaf on $X$.
          We define a new sheaf $\G$, called the sheaf of \emph{discontinuous sections} of $\F$ as follows.
          For each open set $U\subset X$, $\G(U)$ is the set of maps $s:U\to \bigcup_{p\in U}\F_p$ such that for each $p\in U$, $s(p)\in \F_p$.
          Show that $\G$ is a flasque sheaf, and that there is a natural injective morphism $\F\inj \G$.
      \end{enumerate}
    }
\end{enumerate}

\begin{proof}
  (a) Let $X$ be irreducible, $\ol A$ a constant sheaf on $X$.
  Any open subset of an irreducible topological space is connected, so $\ol A(U) \cong A$ for all open sets $U\subset X$.
  Then the restriction map $\ol A(U)\to \ol A(V)$ is the identity $A\to A$, which is in particular surjective.

  (b) The sequence is left exact by (Ex. 1.8), so it suffices to show surjectivity of $\vphi(U):\F(U)\to \F''(U)$.
  First, take $\vphi(s_1)\in \F''(U_1)$ and $\vphi(s_2)\in \F''(U_2)$ such that $\vphi(s_1)|_{U_{12}}=\vphi(s_2)|_{U_{12}}$.
  Then $s_1-s_2\in\F'(U_{12})$, so $\F'$ flasque supplies us with $t_{12}\in \F'(U_1\cup U_2)$ such that $t_{12}|_{U_{12}}=s_1-s_2$.
  Then $s_1\in \F(U_1)$ and $t_{12}+s_2\in \F(U_2)$ glue to a section $s\in \F(U_1\cup U_2)$ such that 
  \begin{align*}
    &s|_{U_1} =s_1,
    &\vphi(s)|_{U_2} =\vphi(t_{12}+s_2) =\vphi(s_2).
  \end{align*}

  Fix $s''\in \F''(U)$.
  By (Ex. 1.4), we can take $s_i\in \F(U_i)$ such that $\vphi(s_i)=s''|_{U_i}$.
  Consider the poset
  \[
    \Sigma = \{(s\in \F(V),V\subset U) ~:~ \vphi(s)= s''|_V\}, \\
  \] 
  ordered by
  \begin{align*}
    (s,V)\leqs (t,W) \iff V\subset W~\&~ s=t|_V.
  \end{align*}
  It is clearly nonempty, as each $(s_i,U_i)\in \Sigma$.
  If $C=\{(t_j,W_j)\}_{j\in J}$ is a nonempty chain, then we can glue to receive a section $t\in \F(\bigcup_{j\in J}W_j)$ such that $\vphi(t)|_{W_j}=\vphi(t_j)=s''|_{W_j}$ for all $j\in J$.
  It follows by uniqueness of gluing in $\F''$ that $\vphi(t)=s''|_{\bigcup_{j\in J}W_j}$, whence $(t,\bigcup_{j\in J}W_j)\in \Sigma$.

  By the proceeding paragraph Zorn's lemma supplies us with a maximal element $(s,V)\in \Sigma$.
  Suppose, by way of contradiction, that $V\neq U$.
  We can take some $U_i$ such that $V\subsetneq V\cup U_i$.
  The construction from the first paragraph supplies us with a section $t\in \F(V\cup U_i)$ such that $t|_V= s$, and $\vphi(t)|_{U_i}=\vphi(s_i)$.
  Then uniquness of gluing in $\F''$ gives us $\vphi(t)=s''|_{V\cup U_i}$, so that $(s,V)<(t,V\cup U_i)\in \Sigma$, contradicting maximality of $(s,V)$.
  Hence, $V=U$, so we have $s\in \F(U)$ such that $\vphi(s)= s''$, as desired.

  (c) The following diagram is exact by (b), whence a trivial diagram chase gives us our result.
  \[
    \begin{tikzcd}
      \F(U)\ar[r,"\vphi(U)"]\ar[d] &\F''(U) \ar[d] \\
      \F(V)\ar[r, "\vphi(V)"]\ar[d] &\F''(V)\ar[r] &0 \\
              0
    \end{tikzcd}
    % \begin{tikzcd}
    %   0\ar[r] &\F'(U)\ar[d]\ar[r] &\F(U)\ar[r,"\vphi(U)"]\ar[d] &\F''(U) \ar[d]\ar[r] &0 \\
    %   0\ar[r] &\F'(V)\ar[d]\ar[r] &\F(V)\ar[r, "\vphi(V)"]\ar[d] &\F''(V)\ar[r] &0 \\
    %           &0&0
    % \end{tikzcd}
  \] 

  (d) Fix open subsets $V\subset U\subset Y$.
  Then the restriction $f_*\F(U)\to f_*\F(V)$ is simply the restriction
  \[
    \F(f^{-1}(U))\to \F(f^{-1}(V)),
  \] 
  which is surjective since $\F$ is flasque.

  (e) Trivial.
\end{proof}

% \begin{enumerate}
%   \item[1.19.] {
%       \emph{Extending a Sheaf by Zero}.
%       Let $X$ be a topological space, $Z$ a closed subset, $i:Z\to X$ the inclusion, $U=X-Z$ the complimentary open subset, and $j:U\to X$ its inclusion.
%       \begin{enumerate}
%         \item Let $\F$ be a sheaf on $Z$.
%           Show that $(i_*\F)_p$ is $\F_p$ if $p\in Z$, and 0 if $p\notin Z$.
%       \end{enumerate}
%     }
% \end{enumerate}
% 
% \begin{proof}
% \end{proof}

\begin{enumerate}
  \item[1.20.] {
      \emph{Subsheaf with Supports}.
      Let $Z$ be a closed subset of $X$, and let $\F$ be a sheaf on $X$.
      We define $\Gamma_Z(X,\F)$ to be the subgroup of $\Gamma(X,\F)$ consisting of all sections whose support (Ex. 1.14) is containing in $Z$.
      \begin{enumerate}
        \item Show that the presheaf $V\mapsto \Gamma_{Z\cap V}(V,\F|_Y)$ is a sheaf.
          It is called the subsheaf of $\F$ with supports in $Z$ and is denoted by $\H_Z^0(\F)$.
        \item Let $U=X-Z$, and let $j:U\to X$ be the inclusion.
          Show there is an exact sequence of sheaves on $X$
          \[
            0\to \H_Z^0(\F)\to \F\to j_*(\F|_U).
          \] 
          Furthermore, if $\F$ is flasque, the map $\F\to j_*(\F|_U)$ is surjective.
      \end{enumerate}
    }
\end{enumerate}

\begin{proof}
  (a)
\end{proof}

% \begin{enumerate}
%   \item[17.] {
%     }
% \end{enumerate}
% 
% \begin{proof}
% \end{proof}
% 
% \begin{enumerate}
%   \item[18.] {
%     }
% \end{enumerate}
% 
% \begin{proof}
% \end{proof}
% 
% \begin{enumerate}
%   \item[19.] {
%     }
% \end{enumerate}
% 
% \begin{proof}
% \end{proof}
% 
% \begin{enumerate}
%   \item[20.] {
%     }
% \end{enumerate}
% 
% \begin{proof}
% \end{proof}
% 
% \begin{enumerate}
%   \item[21.] {
%     }
% \end{enumerate}
% 
% \begin{proof}
% \end{proof}

\end{document}
