\documentclass[12pt]{amsart} 

\input{./latex-preamble/cm-preamble.tex}

%\graphicspath{ {./diagrams/} }

\newtheorem*{lemma}{Lemma}

\begin{document}

{Hartshorne} \hfill {2-7-2025}

\bigskip\bigskip

\begin{center}

{\sc Chapter II.3}

\end{center}

\begin{center}

  {Noah Parker} %\footnote{Collaborated with Kalev Martinson and Frank :).}}
    
\end{center}

\bigskip

\begin{enumerate}
	\item[3.1.] {
      Show that a morphism $f:X\to Y$ is locally of finite type if and only if \emph{every} affine subset $V=\Spec B$ of $Y$, $f^{-1}(V)$ can be covered by open affine subsets $U_j=\Spec A_j$, where each $A_j$ is a finitely generated $B$-algebra.
    }
\end{enumerate}

\begin{proof}
  One direction is clear.
  Suppose conversely that $f:X\to Y$ is locally of finite type, and fix $\Spec A\cong U\subset X$ and $\Spec B\cong V\subset Y$ affine, with $f(U)\subset V$.
  To proceed, we must first prove the following lemma.

  \begin{lemma}
    Fix a sheaf morphism $f:X\to Y$ of finite type, $\Spec A\cong U\subset X$, $\Spec B\cong V\subset Y$, $f(U)\subset Y$ as above, and denote the map of rings associated to $f|_U:U\to V$ by $\vphi:B\to A$.
    There exist $f_{11},\ldots, f_{rs}\in A$ and $g_1,\ldots, g_r\in B$ such that
    \begin{align*}
      \Spec A &= D(f_{11})\cup\cdots \cup D(f_{rs}), \\
      \Spec B &= D(g_1)\cup \cdots \cup D(g_r),
    \end{align*}
    \[
      f(D(f_{ij}))\subset D(g_i),
    \] 
    and the induced map
    \begin{align*}
      \vphi_{g_i}: B_{g_i}\to A_{f_{ij}}
    \end{align*}
    is of finite type.
  \end{lemma}

  \begin{proof}
    We have an affine cover $\{V_i=\Spec B_i\}$ of $X$ such that each $f^{-1}(V_i)$ can be covered by open affines $U_{ij}=\Spec A_{ij}$, where $A_{ij}$ is a finitely generated $B_i$ algebra.
    Fix some $i$ and write
    \begin{align*}
      V_i\cap V &= \bigcup_{D(g_\beta)\subset V_i\cap V}D(g_\beta),
    \end{align*}
    where $D(g_\beta)$ is affine in both $V_i$ and $V$.
    Then $f^{-1}(D(g_\beta))=D(\vphi(g_\beta))$ and fixing some $j$ allows us to write
    \begin{align*}
      U_{ij}\cap U &= \bigcup_{D(f_\alpha)\subset U_{ij}\cap U}D(f_\alpha) \\
             &= \bigcup_{\substack{D(f_\alpha) \subset U_{ij}\cap U \\ D(g_\beta)\subset V_i\cap V}} 
             D(f_\alpha\vphi(g_\beta)),
    \end{align*}
    where each $D(f_\alpha)$ and $D(\vphi(g_\beta))$ is distinguisheed in both $U$ and $U_{ij}$.
    We denote $f_{\alpha\beta}:= f_{\alpha} \vphi(g_\beta)$.
    Then $f|_{D(f_{\alpha\beta})}:D(f_{\alpha\beta}) \to D(g_\beta)$ induces the map $\vphi_{g_\beta}: B_{g_\beta}\to A_{f_{\alpha\beta}}$.

    For any $g_\beta\in B$, $f_\alpha\in A$, and $f_{\alpha\beta}\in A$ as above, we write $g'_\beta\in B_i$, $f'_\alpha\in A_{ij}$, and $f'_{\alpha\beta}\in A_{ij}$ for the corresponding elements which determine the same distinguished subset.
    Then
    \begin{align*}
      (B_i)_{g'_\beta} 
      = \O_{V_i}(D(g'_\beta)) 
      = \O_V(D(g_\beta))
      = B_{g_\beta},
    \end{align*}
    \begin{align*}
      (A_{ij})_{f'_\alpha} 
      = \O_{U_{ij}}(D(f'_\alpha))  
      = \O_U(D(f_\alpha)) 
      = A_{f_\alpha},
    \end{align*}
    and
    \begin{align*}
      (A_{ij})_{f'_{\alpha\beta}}
      = A_{f_{\alpha\beta}}
      = A_{f_\alpha}\otimes_B B_{g_{\beta}}.
    \end{align*}
    Then $A_{ij}$ a finitely generated $B_i$-algebra and $A_{f_\alpha}$ a cyclic $A_{ij}$-algebra gives that $A_{f_\alpha}$ is a finitely generated $B_i$-algebra.
    That is, there exists a surjective map
    \begin{align*}
      B_i[x_1,\ldots, x_{n_\alpha}]~&\rightarrow A_{f_\alpha}.
    \end{align*}
    Right exactness of $-\otimes_B B_{g_\beta}$ gives us a surjective map
    \begin{align*}
      B_{g_\beta}[x_1,\ldots, x_{n_\alpha}]~&\rightarrow A_{f_{\alpha\beta}},
    \end{align*}
    whence $A_{f_{\alpha\beta}}$ is a finitely generated $B_{g_\beta}$-algebra.

    Combining these covers of the $V_i\cap V$ and $U_{ij}\cap U$ gives us a cover $\{D(g_\beta)\}_\beta$ of $\Spec B$, and covers $\{D(f_{\alpha\beta}) \}_\alpha$ of each $f^{-1}(D(g_\beta))=D(\vphi(g_\beta))$, where $\vphi_{g_\beta}:B_{g_\beta}\to A_{f_{\alpha\beta}}$ is of finite type.
    Since $\Spec B$ and $D(\vphi(g_\beta))$ are affine, we may assume each of these covers is finite, completing our result.
  \end{proof}

  Thus, it suffices to show the following lemma.

  \begin{lemma}
    Let $\vphi:B\to A$ be a morphism of rings such that $\vphi_i:B\to A_{f_i}$ is of finite type for each $1\leqs i\leqs r$, where $(f_1,\ldots, f_r)=(1)$.
    Then $\vphi$ is of finite type.
  \end{lemma}

  \begin{proof}
    Take $\{a_{ij}=a'_{i j}/f_i^{e_{ij}}\}_{j=1}^{r_i}$ to be a set of generators for $A_{f_i}$ as a $B$-algebra. %, so that $\{a_{ij}'\}_{j=1}^{s_i}\cup\{f_i^{-1}\}$ is another set of generators for
    Without loss of generality, $r_i=r$ for all $1\leqs i\leqs r$.
    Define
    \[
      A' := \vphi(B)[a'_{ij}~:~1\leqslant i,j\leqs r],
    \] 
    noting that
    \begin{align*}
      A'_{f_i} &= \vphi(B)[f_i^{-1},a'_{ij}~:~\leqslant i,j\leqs r]= A_{f_i}.
    \end{align*}
    Now, consider the quotient $A/A'$.
    It suffices to show that $A/A'=0$.
    For any prime ideal $\p\in \Spec A$, we can choose $i$ such that $f_i\notin \p$.
    Then
    \begin{align*}
      (A/A')_\p &= \frac{A_\p}{A'_\p} \\
                &= \frac{(A_{f_i})_\p} {(A'_{f_i})_\p} \\
                &= \left(\frac{A_{f_i}}{A_{f_i}}\right)_\p \\
                &= 0_\p \\
                &= 0
    \end{align*}
    gives us that in fact $A/A'=0$, since being zero is a local condition.
    We conclude that $A$ is a finitely generated $B$-algebra, as desired.
  \end{proof}
\end{proof}
 
 \begin{enumerate}
 	\item[3.2.] {
       A morphism $f:X\to Y$ of schemes is \emph{quasi-compact} if there is a cover of $Y$ by open affines $V_i$ such that $f^{-1}(V_i)$ is quasi-compact for each $i$.
       Show that $f$ is quasi compact if and only if for \emph{every} open affine subset $V\subset Y$, $f^{-1}(V)$ is quasi-compact.
     }
 \end{enumerate}
 
 \begin{proof}
   One implication is clear.
   Conversely, suppose there exists a cover $\{V_i=\Spec B_i\}$ of $Y$ by open affines such that $f^{-1}(V_i)$ is quasi-compact for each $i$, and take an open affine $V=\Spec B\subset Y$.
   Fix $i$ and write 
   \begin{align*}
     V\cap V_i&= \bigcup_j D(g_{ij}),
   \end{align*}
   where we range over $D(g_{ij})\subset V\cap V_i$ which are affine in both $V$ and $V_i$.
   Then
   \begin{align*}
     V&= \bigcup_{i,j}D(g_{ij}) = \bigcup_{1\leqs i,j\leqs n}D(g_{ij})
   \end{align*}
   by quasi-compactness of $V_i$.
   A finite union of compact sets is compact, so it suffices to show the following lemma.%that $f^{-1}(D(g))$ is compact for each $g\in B_i$.

   \begin{lemma}
     Let $f:X\to Y$ be a map of schemes, and $\Spec A\cong U\subset Y$ an affine open such that $f^{-1}(U)$ is quasi-compact.
     For any $h\in A$, $f^{-1}(D(h))$ is also quasi-compact.
   \end{lemma}

   \begin{proof}
     Take a cover $\{U_\alpha\}_\alpha$ of $f^{-1}(D(h))$, and note that
     \begin{align*}
       f
     \end{align*}
   \end{proof}
 \end{proof}
 
 \begin{enumerate}
 	\item[3.3.] {
       $(*)$
       \begin{enumerate}
         \item Show that a morphism $f:X\to Y$ is of finite type if and only if it is locally of finite type and quasi-compact.
         \item Conclude from this that $f$ is of finite type if and only if for \emph{every} open affine subset $V=\Spec B$ of $Y$, $f^{-1}(V)$ can be covered by a finite number of open affines $U_j=\Spec A_j$, where each $A_j$ is a finitely generated $B$-algebra.
         \item Show also if $f$ is of finite type, then for \emph{every} open affine subset $U=\Spec A\subset f^{-1}(V)$, $A$ is a finitely generated $B$-algebra.
       \end{enumerate}
     }
 \end{enumerate}
 
 \begin{enumerate}
   \item[3.4.] {
       Show that a morphism $f:X\to Y$ is finite if and only if for \emph{every} open affine subset $V=\Spec B$ of $Y$, $f^{-1}(V)$ is affine, equal to $\Spec A$, where $A$ is a finite $B$-module.
     }
 \end{enumerate}
 
 \begin{proof}
   Fix an open affine cover $\{V_i\cong \Spec B_i\}$ of $Y$ such that $f^{-1}(V_i)\cong \Spec A_i$ is affine, and each $A_i$ is a finite $B_i$-module.
 \end{proof}
 
 \begin{enumerate}
   \item[3.6.] {
       Let $X$ be an integral scheme.
       Show that the local ring $\O_\xi$ of the generic point $\xi$ of $X$ is a field.
       It is called the \emph{function field} of $X$, and is denoted by $K(X)$.
       Show also if $U=\Spec A$ is any open affine subset of $X$, then $K(X)$ is isomorphic to the quotient field of $A$.
     }
 \end{enumerate}
 
 \begin{proof}
   Fix $U=\Spec A\subset X$ open affine.
   Then $\Cl_U(\{\xi\})=\{\xi\}^-\cap U=U$ implies that $\xi$ is the minimal prime ideal of $U$.
   That is, $\xi=(0)\in \Spec A$.
   Then $K(X)= A_{(0)}$ is the quotient field of $A$.
 \end{proof}
\begin{enumerate}
	\item[3.9.] {
      \emph{The Topological Space of a Product.}
      Recall that in the category of varieties, the Zariski topology on the product of two varieties is not equal to the product topology.
      Now, we see that in the category of schemes, the underlying point set of a product of schemes is not even the product set.
      \begin{enumerate}
        \item Let $k$ be a field, and let $\A^1_k=\Spec k[x]$ be the affine line over $k$.
          Show that $\A_k^1\times_{\Spec k}\A_k^1\cong \A_k^2$, and show that the underlying point set of the product is not the product of the underlying point set of the factors (even if $k$ is algebraically closed).
        \item Let $k$ be a field with $s$ and $t$ indeterminates over $k$.
          Then $\Spec k(s)$, $\Spec k(t)$, and $\Spec k$ are all one point spaces.
          Describe the product scheme $\Spec k(s)\times_{\Spec k}\Spec k(t)$.
      \end{enumerate}
    }
\end{enumerate}

\begin{proof}
  (a) We have that $k[x]\otimes_k k[x]\cong k[x,y]$ as $k$-algebras, so $\A_k^1\times_{\Spec k}\A_k^1\cong \A_k^2$ as schemes over $k$.
  Fix $k=\CC$, and consider the generic points of $\A_k^2$.
  %If there were a bijection between $\A_k^2$ and the set theoretic product, then this would give us a bijection of generic points, and thus a bijection of irreducible components.
  %There is an injection of point sets $f:\A_k^1\times\A_k^1\to \A_k^2$ given by $(\p,\q)\mapsto \p^e + \q^e$.
  A bijection of sets would give us a bijection of generic points, and thus a bijection of irreducible polynomials.
  This is clearly false, so that $\A_k^2\neq \A_k^1\times \A_k^1$ as sets.

  (b) Fix $A=k(s)\otimes_k k(t)$, so that the product scheme is given by $X=\Spec A$.
  Consider the ideal $\p=(s\otimes 1 +1\otimes t)\subset A$.
  Clearly $\p\neq (0)$.
  If $\p=(1)$, then we have
  \begin{align*}
    1\otimes 1 &= (s\otimes 1 + 1\otimes t)\left(\sum_{i=1}^n \frac{f_i(s)}{p_i(s)}\otimes \frac{g_i(t)}{q_i(t)}\right) \\
      &= \sum_{i=1}^n\frac{sf_i(s)}{p_i(s)}\otimes \frac{g_i(t)}{q_i(t)} +
      \frac{f_i(s)}{p_i(s)}\otimes \frac{tg_i(t)}{q_i(t)}.
  \end{align*}
\end{proof}

\begin{enumerate}
	\item[3.10.] {
      \emph{Fibres of a morphism.}
      \begin{enumerate}
        \item If $f:X\to Y$ is a morphism and $y\in Y$ a point, show that $\ssp(X_y)$ is homeomorphic to $f^{-1}(y)$ with the induced topology.
        \item Let $X=\Spec k[s,t]/(s-t^2)$, $Y=\Spec k[s]$, and $f:X\to Y$ the morphism defined by $s\mapsto s$.
          If $y\in Y$ is a point $a\in K$ with $a\neq 0$, show that the fibre $X_y$ consists of two points, with residue field $k$.
          If $y\in Y$ corresponds to $0\in k$, show that the fibre $X_y$ is a nonreduced one-point scheme.
          If $\eta$ is the generic point of $Y$, show that $X_\eta$ is a one-point scheme, whose residue field is an extension of degree two of the residue field of $\eta$. (Assume $k$ algebraically closed.)
      \end{enumerate}
    }
\end{enumerate}

\begin{proof}
  (a) We begin by considering the affine case, $Y=\Spec A$, $X=\Spec B$, and $f^\sharp(Y)=\vphi:A\to B$.
  An identical method to that of Ex. 2.1 gives us the following lemma.
  \begin{lemma}
    Let $A$ be a ring and $\phi:A\to S^{-1}A$ the inclusion into its localization.
    Then $\phi^*:\Spec (S^{-1}A)\to \Spec A$ is a homeomorphism onto its image in $\Spec A = X$.
    We denote this image $S^{-1} X$.
  \end{lemma}
  % % Additionally, $\vphi_y:A_y\to (B_A)_y$ gives us the following diagram.
  % % \[
  % %   \begin{tikzcd}
  % %     A\ar[r,"\vphi"]\ar[d,"\phi_A"'] & B_A\ar[d,"\phi_B"] \\
  % %     A_y\ar[r,"\vphi_y"'] & (B_A)_y
  % %   \end{tikzcd}
  % % \] 
  % % Taking $\Spec$ gives us
  % % Since $\vphi_y$ is a local ring, $\vphi_y$ factors to a map
  % % \[
  % %   \ol{\vphi_y}:B_A
  % % \] 
  The next lemma is easy, but worth proving.
  \begin{lemma}
    Let $f:A\to B$ be a ring morphism, $X:= \Spec A$, $Y:=\Spec B$, and $S$ a multiplicative subset of $A$.
    Then denoting $S^{-1}B =f(S)^{-1}B\cong B_A\otimes_A S^{-1}A$ and identifying spectra as in the prior lemma, 
    \[
      S^{-1}f^*:\Spec (S^{-1}B)\to \Spec(S^{-1}A)
    \]
    is the restrition of $f^*$ to $S^{-1}Y$, and $S^{-1}Y={f^*}^{-1}(S^{-1}X)$.
  \end{lemma}

  \begin{proof}
    We have the following commutative diagram.
    \[
      \begin{tikzcd}
        A \ar[r,"f"]\ar[d,"\phi_A"'] & B\ar[d,"\phi_B"] \\
        S^{-1}A\ar[r,"S^{-1}f"']& S^{-1}B
      \end{tikzcd}
    \] 
   Applying the contravariant functor $\Spec$, we get a diagram of topological spaces.
   \[
     \begin{tikzcd}
        X & Y\ar[l,"f^*"']\\
        \Spec(S^{-1}A)\ar[u,"\phi_A^*"] 
                      & \Spec(S^{-1}B)\ar[u,"\phi_B^*"']\ar[l,"S^{-1}f^{*}"]
     \end{tikzcd}
   \] 
   Then 
   \[
     f^*(S^{-1}Y) = \phi_A^*(S^{-1}f^*(\Spec(S^{-1}B))\subset S^{-1}X
   \]
   allows us to restrict to the following diagram.
   %\[
   %  \begin{tikzcd}
   %     S^{-1}X \ar[d,shift left = 1ex,"(\phi_A^*)^{-1}"] 
   %     & S^{-1}Y\ar[l,"f^*|_{S^{-1}Y}"']
   %     \ar[d, shift right = 1ex,"(\phi_B^*)^{-1}"'] \\
   %     \Spec(S^{-1}A)\ar[u,shift left = 1ex,"\phi_A^*"]
   %                   & \Spec(S^{-1}B)\ar[u,shift right = 1ex,"\phi_B^*"']\ar[l,"S^{-1}f^{*}"]
   %  \end{tikzcd}
   %\] 
   \[
     \begin{tikzcd}
        S^{-1}X & S^{-1}Y\ar[l,"f^*|_{S^{-1}Y}"'] \\
        \Spec(S^{-1}A)\ar[u,"\phi_A^*"]
                      & \Spec(S^{-1}B)\ar[u,"\phi_B^*"']\ar[l,"S^{-1}f^{*}"]
     \end{tikzcd}
   \] 
   By the preceding lemma, $\phi_A^*$ and $\phi_B^*$ are heomeomorphisms onto their image, whence the result follows.
  \end{proof}

  One last lemma precedes the proof of the desired statement.

  \begin{lemma}
    Let $\a$ be an ideal of $A$ and let $\b=\a B$ be its extension in $B$.
    Let $f:A/\a\to B/\b$ be the homomorphism induced by $f$.
    If $\Spec (A/\a)$ is identified with its canonical image $V(\a)\subset X$, and $\Spec (B/\b)$ with $V(\b)\subset Y$, show that $\ol{f}^*=f^*|_{V(\b)}$.
  \end{lemma}

  \begin{proof}
    We have the following commutative diagram.
    \[
      \begin{tikzcd}
        A \ar[r,"f"]\ar[d,"\pi_A"'] & B\ar[d,"\pi_B"] \\
        A/\a\ar[r,"\ol{f}"']& B/\b
      \end{tikzcd}
    \] 
    Once again applying Spec,
    \[
      \begin{tikzcd}
        X & Y\ar[l,"f^*"']\\
        \Spec(A/\a)\ar[u,"\pi_A^*"] 
          & \Spec(B/\b)\ar[u,"\pi_B^*"']\ar[l,"\ol{f}^*"]
      \end{tikzcd}
    \] 
    and restricting as before gives us our last diagram.
    \[
      \begin{tikzcd}
        V(\a) & V(\b)\ar[l,"f^*|_{V(\b)}"'] \\
        \Spec(A/\a)\ar[u,"\pi_A^*"]
              & \Spec(B/\b)\ar[u,"\pi_B^*"'] \ar[l,"\ol{f}^*"]
      \end{tikzcd}
    \] 
    By Exercise 2.18, $\pi_A^*$ and $\pi_B^*$ are homeomorphisms onto their images $V(\a)$ and $V(\b)$, so that the result follows.
  \end{proof}

  Finally, we set $X=\Spec B$, $Y= \Spec A$, and fix $y=\p\in \Spec A$.
  Clearly, we have homeomorphisms
  \begin{align*}
    X_\p&=\Spec (B\otimes_A k(\p)) \\
       &\cong \Spec(B\otimes_A A_\p/\m_\p) \\
       &\cong \Spec(B_{A_\p}/\p B_{A_\p}) \\
       &\cong V(\p B_{A_\p}),
  \end{align*}
  where the last equality follows from Exercise 2.18 as before.
  Then equalities
  \begin{align*}
       &\cong V(\vphi_\p (\m_\p)B_{A_\p}) \\
       &\cong (\vphi_\p^*)^{-1}(V(\m_\p)) \\
       &\cong f_\p^{-1}(\m_\p) \\
       &\cong f^{-1}(\p).
  \end{align*}
  follow from minimality of the extension of an ideal, maximality of $\m_\p\lideal A_\p$, and the second lemma respectively.\footnote{I originally wrote this out a while ago, so I hadn't written it up again, let alone in simplied form, when we had our meeting. For some reason I thought (b) was the interesting part lol.}

  %(a) The affine case is Ex. 3.20 in Atiyah-MacDonald. %\footnote{I did it on paper, and it's a tad boring to write out. Just a series of commutative diagrams, and a repeat argument from Ex 2.1 of Hartshorne.} 
  Fix affine open covers $\{U_i=\Spec A_i\}$ of $X$ and $\{V_j=\Spec B_j\}$ of $Y$.
  Let $g:\Spec k(y)\to Y$ be the natural map, giving $\Spec k(y)$ the structure of a $Y$-scheme.
  We have 
  \[
    k(y)= \O_{Y,y}/m_y\O_{Y,y}\cong (B_j)_y/y(B_j)_y := k_j(y)
  \] 
  for all $y\in Y_j$.

  Then $X_y$ is the gluing of the spaces $f^{-1}(Y_j)\times_{Y_j} \Spec k_j(y)$, over all $Y_j\ni y$.
  We can write 
  \begin{align*}
    X_i\cap f^{-1}(Y_j)= \bigcup_{\substack{g_{i j k}\in X_i \\ D_i(g_{i j k})\subset f^{-1}(Y_j)}} D_i(g_{ij k})
  \end{align*}
  as a union of affines.
  Defining $f_{i j k}:=f|_{D_i(g_{i j k})}:D_i(g_{ i j k})\to Y_j$, the affine case gives us that
  \begin{align*}
    X_y &= \bigcup_{\substack{i,\,j,\, g_{ij k}\in X_i \\ D_i(g_{i j k})\subset f^{-1}(Y_j)}}
    D_i(g_{i j k})\times_{Y_j} \Spec k_j(y) \\
        &= \bigcup_{i,\, j,\, k} D_i(g_{i j k})_y \\
        &= \bigcup_{i,\, j,\, k} f_{i j k}^{-1}(y) \\
        &= f^{-1}(y)\cap \bigcup_{i, \, j, \,k} D_i(g_{ij k}) \\
        &= f^{-1}(y).
  \end{align*}

  (b) We have that $X_a=\Spec A_a$, where
  \begin{align*}
    A_a &= \frac{k[s,t]}{(s-t^2)}\otimes_{k[s]}\frac{k[s]_{(s-a)}}{(s-a)k[s]_{(s-a)}} \\
        &\cong k[t]\otimes_{k[t^2]}\frac{k[t^2]}{(a-t^2)} \\
        &\cong \frac{k[t]}{(a-t^2)}.
  \end{align*}
  Then $\Spec A_a\cong V(a-t^2)=\{(\sqrt{a}+ t,\sqrt{a}-t)\}\subset \Spec k[t]$.
  If $a\neq 0$, then this is a two point set, with residue fields given by
  \begin{align*}
    k_a(\sqrt{a}-t) &=\frac{k[t]}{(\sqrt{a}-t)}\cong k,\\
    k_a(\sqrt{a}+t) &=\frac{k[t]}{(\sqrt{a}+t)}\cong k.
  \end{align*}
  If $a=0$, then $\Spec A_0=\{t\}$ is singleton, and $t\in A_0$ is a nilpotent.

  Finally, we consider 
  \begin{align*}
    A_\eta &\cong \frac{k[s,t]}{(s-t^2)}\otimes_{k[s]}\frac{k[s]_{(0)}}{(0)k[s]_{(0)}} \\
           &\cong k[t]\otimes_{k[t^2]}k(t^2) \\
           &\cong k(s)[\sqrt{s}].
  \end{align*}
  Then $A_\eta$ is a PID, so its only ideals are of the form $(f(\sqrt{s}))$ for $f(\sqrt{s})= f_1(s)+f_2(s)\sqrt{s}$.
  Then $f\ol{f}(\sqrt{s})\in k(s)$ defined in the obvious manner is invertible whenever $f\neq 0$, so $(f(\sqrt{s}))=0,A_\eta$ gives us that $\Spec A_\eta$ is singleton.
  Furthermore, $(A_\eta)_{(0)}\cong k(\sqrt{s})$, which is a degree two extension over $k(\eta)=k(s)$, as desired.
\end{proof}

\begin{enumerate}
	\item[3.11.] {
     $(*)$ \emph{Closed Subschemes.}
     \begin{enumerate}
       \item Closed immersions are stable under base extension: if $f:Y\to X$ is a closed immersion, and if $X'\to X$ is any morphism, then $f':Y\times_X X' \to X'$ is also a closed immersion.
       \item If $Y$ is a closed subscheme of an affine scheme $X=\Spec A$, then $Y$ is also affine, and in fact $Y$ is the closed subscheme determined by a suitable ideal $\a\subset A$ as the image of the closed immersion $\Spec A/\a\to \Spec A$.
         [\emph{Hints}: First show that $Y$ can be covered by a finite number of open affine subsets of the form $D(f_i)\cap Y$, with $f_i\in A$.
         By adding some more $f_i$ with $D(f_i)\cap Y$ if necessary, show that we may assume the $D(f_i)$ cover $X$.
         Next, show that $f_1,\cdots, f_r$ generate the unit ideal of $A$.
         Then use Ex. 2.17b to show that $Y$ is affinem and Ex. 2.18d to show that $Y$ comes from an ideal $\a\subset A$]
         \emph{Note}: We will prove this with sheaves of ideals later.
       \item Let $Y$ be a closed subset of a scheme $X$, and give $Y$ the reduced induced sub-scheme structure.
         If $Y'$ is any other closed subscheme of $X$ with the same underlying topological space, show that the closed immersion $Y\to X$ factors through $Y'$.
         We express this property by saying that the reduced induced structure is the smallest subscheme structure on a closed subset.
       \item Let $f:Z\to X$ be a morphism.
         Then there is a unique closed subscheme $Y$ of $X$ with the following property:
         the morphism $f$ factors through $Y$, and if $Y'$ is any other closed subscheme of $X$ through with $f$ factors, then $Y\to X$ factors throuogh $Y'$ also.
         We call $Y$ the \emph{scheme-theoretic image} of $f$.
         If $Z$ is a reduced scheme, then $Y$ is just the reduced induced structure on the closure of the image $f(Z)$.
     \end{enumerate}
    }
\end{enumerate}
 
\begin{enumerate}
 	\item[3.12.] {
      \emph{Closed subschemes of $\Proj S$.}
      \begin{enumerate}
        \item Let $\vphi:S\to T$ be a surjective homomorphism of graded rings, preserving degrees.
          Show that the open set $U$ is equal to $\Proj T$, and the morphism $f:\Proj T\to \Proj S$ is a closed immersion.
        \item If $I\subset S$ is a homogeneous ideal, take $T=S/I$ and let $Y$ be the closed subscheme of $X=\Proj S$ defined as image of the closed immersion $\Proj S/I\to X$.
          Show that different homogeneous ideals can give rise to the same closed subscheme.
          For example, let $d_0$ be an integer and let $I'=\oplus_{d\geqs 0}I_d$.
          Show that $I$ and $I'$ determine the same subscheme.\\
          We will see later that every closed subscheme of $X$ comes from a homogeneous ideal $I$ of $S$ (at least in the case where $S$ is a polynomial ring over $S_0$).
      \end{enumerate}
    }
\end{enumerate}
 
\begin{proof}
  (a) Denote $Y=\Proj S$ and $X=\Proj T$.
  We have $\vphi(S_+)= T_+$, so that $U=X$ by definition.
  Fix homogeneous $g\in S_+$.
  Surjectivity of $\vphi:S\to T$ implies $\vphi_{g}:S_{g}\to T_{\vphi(g)}$ is surjective.
  Then $\vphi$ degree preserving gives us that $(S_g)_d=\vphi_g^{-1}((T_g)_d)$ for all $d\geqs 0$, whence $\vphi_g:S_{(g)}\to T_{(\vphi(g))}$ is surjective.
  It follows that $f^\sharp:\O_X\to f_*\O_Y$ is surjective.

  Surjectivity of $\vphi$ gives us $\vphi(\vphi^{-1}(\b))$ for all $\b\trianglelefteq T$,  whence
  \[
    \p\supset \b \iff \vphi^{-1}(\p)\supset \vphi^{-1}(\b).
  \] 
  Then
  \begin{align*}
    f(V(\b)) &= V(\vphi^{-1}(\b))\cap f(X)
  \end{align*}
  shows that, in particular,
  \[
    f(X) = V(\ker\vphi)\cap f(X)\subset V(\ker\vphi).
  \] 
  Take $\p\in V(\ker\vphi)$, and $a\in \vphi^{-1}(\vphi(\p))$.
  Then we have $a'\in \p$ with $\vphi(a)=\vphi(a')$, whence $a-a'\in \ker\vphi\subset \p$ implies $a\in \p$.
  Thus, $\p=\vphi^{-1}(\vphi(\p))\in f(X)$ gives us $f(X)=V(\ker\vphi)$.
  We conclude that 
  \[
    f(V(\b)) = V(\ker\vphi + \vphi^{-1}(\b))
  \] 
  is closed in $\Proj S$, so that $f$ is a homeomorphism onto the closed set $f(X)=V(\ker\vphi)$.

  (b) Let $\pi: S\to S/I$ and $\pi':S\to S/I'$ be the natural projections.
  Since $I'\subset I=\ker\pi$, we can factor $\pi=\vphi\pi'$, where $\vphi:S/I'\to S/I$ is the identity $\vphi_d:S_d/I'_d=S_d/I_d\to S_d/I_d$ for $d\geqs d_0$.
  Then Ex. 2.14(b) gives us that $\vphi^*:\Proj (S/I)\to \Proj (S/I')$ is an isomorphism of sheaves, so $(\pi')^*(\Proj (S/I'))=\vphi^*\pi^*(\Proj (S/I))\cong \pi^*(\Proj(S/I))$ give the same closed subscheme structure.
\end{proof}

\begin{enumerate}
 	\item[3.13.] {
       \emph{Properties of Morphisms of Finite Type}
       \begin{enumerate}
         \item A closed immersion is a morphism of finite type.
         \item A quasi-compact open immersion is of finite type.
         \item A composition of two morphisms of finite type is of finite type.
         \item Morphisms of finite type are stable under base extension.
         \item If $X$ and $Y$ are schemes of finite type over $S$, then $X\times_S Y$ is of finite type over $S$.
         \item If $X\xrightarrow{f}Y\xrightarrow{g}Z$ are two morphisms, and if $f$ is quasi-compact, and $g\circ f$ is of finite type, then $f$ is of finite type.
         \item If $f:X\to Y$ is a morphism of finite type, and if $Y$ is noetherian, then $X$ is noetherian.
       \end{enumerate}
     }
\end{enumerate}

\begin{proof}
  (a) Let $f:X\to Y$ be a closed immersion, $\{U_i=\Spec A_i\}_{i\in I}$ an affine open cover of $X$, and fix $V=\Spec B\subset Y$ open affine.
  Then
  \begin{align*}
    f^{-1}(V)&= \bigcup_{i\in I} f^{-1}(V)\cap U_i \\
             &= \bigcup_{\substack{i\in I,~g_{ij}\in A_i \\ D_i(g_{ij}) \subset f^{-1}(V)}} D_i(g_{ij})
  \end{align*}
  is a union of open affines $D_i(g_{ij})=\Spec (A_i)_{g_{ij}}$.

  We have that $f^\sharp:\O_Y\to f_*\O_X$ is surjective.
  That is, $f^\sharp_\q:B_\q\to A_{B_\q}$ is surjective for each prime ideal $\p$ of $B$.
  Then
  \begin{align*}
    f(D_{i}(g_{ij})) &= \{f^\sharp(V)^{-1}(\p)\in \Spec B:\p\lideal A_i, ~\p\not\ni g_{ij}\} \\
                       &= \{\}
  \end{align*}

  (d) Let $f:X\to Y$ be a scheme of finite type, and $Y\to Y'$ a map of schemes.
\end{proof}

\begin{enumerate}
  \item[3.14.] {
      $(*)$ If $X$ is a scheme of finite type over a field, show that the closed points of $X$ are dense.
      Give an example to show that this is note true for arbitrary schemes.
    }
\end{enumerate}

\begin{enumerate}
  \item[3.15.] {
      $(*)$ Let $X$ be a scheme of finite type over a field $k$ (not necessarily algebraically closed).
      \begin{enumerate}
        \item Show that the following three conditions are equivalent (in which case we say that $X$ is \emph{geometrically irreducible}).
          \begin{enumerate}
            \item $X\times_k \ol{k}$ is irreducible, where $\ol{k}$ is the algebraic closure of $k$.
            \item $X\times_k k_s$ is irreducible, where $k_s$ denotes the sperable closure of $k$.
            \item $X\times_k K$ is irreducible for every extensions $K/k$.
          \end{enumerate}
        \item Show that the following three conditions are equivalent (in which case we say $X$ is \emph{geometrically reduced}).
          \begin{enumerate}
            \item $X\times_k \ol{k}$ is reduced.
            \item $X\times_k k_p$ is reduced, where $k_p$ denotes the perfect closure of $k$.
            \item $X\times_k K$ is reduced for all extensions $K/k$.
          \end{enumerate}
          \item We say that $X$ is \emph{geometrically integral} if $X\times_k \ol{k}$ is integral.
            Note that, by (a) and (b), this implies $X=X\times_k k$ is integral.
            Give examples of integral schemes which are neither geometrically irreducible nor geometrically reduced.
      \end{enumerate}
    }
\end{enumerate}

\begin{enumerate}
  \item[3.20.] {
      $(*)$ \emph{Dimension}. Let $X$ be an integral scheme of finite type over a field $k$ (not necessarily closed).
      Use results about varieties to prove the following.
      \begin{enumerate}
        \item For any closed point $p\in X$, $\dim X=\dim \O_P$, where for rings we always mean the Krull dimension.
        \item Let $K(X)$ be the function field of $X$.
          Then $\dim X=\trd K(X)/k$.
        \item If $Y$ is a closed subset of $X$, then $\codim(Y,X)=\inf{\dim \O_{X,p}|p\in Y}$.
        \item If $Y$ is a closed subset of $X$, then $\dim Y+\codim (Y,X)=\dim X$.
        \item If $U$ is a nonempty open subset of $X$, then $\dim U=\dim X$.
      \end{enumerate}
    }
\end{enumerate}

\begin{proof}
\end{proof}

% \begin{enumerate}
%   \item[2.13.] {
%     }
% \end{enumerate}
% 
% \begin{proof}
% \end{proof}
% 
% \begin{enumerate}
%   \item[19.] {
%     }
% \end{enumerate}
% 
% \begin{proof}
% \end{proof}
% 
% \begin{enumerate}
%   \item[20.] {
%     }
% \end{enumerate}
% 
% \begin{proof}
% \end{proof}
% 
% \begin{enumerate}
%   \item[21.] {
%     }
% \end{enumerate}
% 
% \begin{proof}
% \end{proof}

\end{document}
